### 2023-10-05 3.Design/dataset.tex
New figures and more

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{datasets/airline}
  \caption{Graphical representation of the airline passenger dataset. The vertical lines represent a full year.}
  \label{fig:afGraph}
\end{figure}

@@

\begin{itemize}
  \item \ac{LSTM} with four hidden states ($n_h=4$) and an input with feature size of one and two time steps.
\end{itemize}

The model used to solve this problem is an \ac{LSTM} with four hidden states, a batch size of one and uses two time steps.

>>>>

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{datasets/airline}
  \caption{the airline dataset in a grphic. This is the curve that the regression is trying to reproduce. The vertical lines represent a full year.}
  \label{graph:airline}
\end{figure}

@@

\begin{itemize}
  \item An \ac{LSTM} with four hidden states ($n_h=4$) and an input with feature size of one and two time steps.
  \item A Dense layer with an output size of one.
\end{itemize}

\Cref{fig:airlineModel} is a graphical representation of the model just described.

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{datasets/airlineModel}
  \caption{Model used to solve the airline passengers problem}
  \label{fig:airlineModel}
\end{figure}
